\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
fix missing word "code" after mcrt
hypen

There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis framework, 
can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 
products include ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
geometry into formats usable by MCRT codes, with examples including DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if that model is comprised of a 
large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT can be a cumbersome task. The existent set of software does not 
provide a complete set of tools to efficiently create complex geometries.

This paper is structured as follows, first a brief radiation transport focused introduction to computer descriptions of geometry, followed by an explanation of the design 
and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 
FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite complex system consisting of components drawn from 
all the supported  geometry input files formats.

>>>>

There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis framework, 
can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 
products include ESABASE2~\cite{ESABASE2} and FASTRAD~\cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
geometry into formats usable by MCRT codes, with examples including DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if that model is comprised of a 
large number of parts. Exporting, assigning material to, and placing the STL components into the MCRT code can be a cumbersome task. The existent set of software does not 
provide a complete set of tools to efficiently create complex geometries.

This paper is structured as follows, first a brief radiation transport-focused introduction to computer descriptions of geometry, followed by an explanation of the design 
and implementation of \PYGEOMETRY{}. The sections that follow describe how \PYGEOMETRY{} can be used to perform rapid geometric modelling, conversion from 
FLUKA to GDML, GDML to FLUKA and CAD to GDML. The paper concludes with an example of a composite complex system consisting of components drawn from 
all the supported  geometry input files formats.
